Effects of Reynolds Number on the Performance and Near-Wake of a Vertical-Axis Cross-Flow Turbine

### 2015-04-18 paper.tex
Add description of Blackwell et al and Bravo et al to intro

>>>>

Blackwell et al. investigated the effects of Reynolds number on the performance
of a 2 m diameter Darrieus vertical-axis cross-flow wind turbine with NACA 0012
blades \cite{Blackwell1976}. By varying wind tunnel speed, the turbine was made
to operate at approximately constant blade chord Reynolds number $Re_c$ ranging
from $1 \times 10^5$ to $3 \times 10^5$. In this regime the turbine power
coefficient $C_P$ was shown to be sensitive to $Re_c$, with sensitivity
diminishing at the higher Reynolds numbers, especially for turbines of lower
solidity ($Nc/R$, where $N$ is the number of blades and $R$ is the turbine's
maximum radius). More recently, Bravo et al. observed power coefficient of a
straight-bladed VAWT to become Reynolds number independent at $Re_c \approx 4
\times 10^5$.
